Variants of G\"{o}del's Ontological Proof \\ in a Natural Deduction Calculus

### 2016-11-08 Papers/InProgress/NaturalDeduction/GodProof-ND.tex
Boldface logic names

The aim of this paper is to present detailed formalizations of variants of ontological arguments in a natural deduction calculus. For a comprehensive introduction to natural deduction, the reader can consult \citep{prawitz} or \citep{gabbay}. The natural deduction calculus proposed and used in this paper is an extension of a standard natural deduction calculus for (non-modal) higher-order logic \citep{BenzmuellerBrownKohlhase} with new introduction and elimination rules for modal operators (as presented in Section \ref{sec:calculus}). This calculus is sound and complete relative to the non-modal calculus extended with Axiom K and the Necessitation rule (as demonstrated in Subsection \ref{sec:compl-sound}). There are many higher-order logics \citep{BenzmuellerBrownKohlhase} and higher-order modal logics \citep{Muskens}. The calculus proposed here can be regarded as a minimalistic calculus for a rigid higher-order modal logic K without extensionality principles. With additional axioms for stronger modal logics, such as KB and S5, this calculus is sufficient to achieve the stated aim.

@@

\begin{small}
\begin{prooftree}
\AXC{$ $} \RightLabel{1}
\UIC{$\pos \ex x. G(x)$} 
 \AXC{$\subproof_5$}\dashedLine
 	\UIC{$\pos \ex x. G(x) \imp \pos \nec \ex x. G(x)$} \RightLabel{$\imp_E$}
 \BIC{$\pos \nec \ex x. G(x)\scott$} 
			\AXC{S5 Iteration Principle} \dashedLine
			\UIC{$\pos \nec \ex x. G(x) \imp \nec \ex x. G(x)$}\RightLabel{$\imp_E$}
		\BIC{$\nec \ex x. G(x)$} \RightLabel{$\imp_I^1$}
		\UIC{$\pos \ex z. G(z) \imp \nec \ex x. G(x)$}
\end{prooftree}
\end{small}

>>>>

The aim of this paper is to present detailed formalizations of variants of ontological arguments in a natural deduction calculus. For a comprehensive introduction to natural deduction, the reader can consult \citep{prawitz} or \citep{gabbay}. The natural deduction calculus proposed and used in this paper is an extension of a standard natural deduction calculus for (non-modal) higher-order logic \citep{BenzmuellerBrownKohlhase} with new introduction and elimination rules for modal operators (as presented in Section \ref{sec:calculus}). This calculus is sound and complete relative to the non-modal calculus extended with Axiom K and the Necessitation rule (as demonstrated in Subsection \ref{sec:compl-sound}). There are many higher-order logics \citep{BenzmuellerBrownKohlhase} and higher-order modal logics \citep{Muskens}. The calculus proposed here can be regarded as a minimalistic calculus for a rigid higher-order modal logic {\bf K} without extensionality principles. With additional axioms for stronger modal logics, such as {\bf KB} and {\bf S5}, this calculus is sufficient to achieve the stated aim.

@@

\begin{small}
\begin{prooftree}
\AXC{$ $} \RightLabel{1}
\UIC{$\pos \ex x. G(x)$} 
 \AXC{$\subproof_5$}\dashedLine
 	\UIC{$\pos \ex x. G(x) \imp \pos \nec \ex x. G(x)$} \RightLabel{$\imp_E$}
 \BIC{$\pos \nec \ex x. G(x)\scott$} 
			\AXC{{\bf S5} Iteration Principle} \dashedLine
			\UIC{$\pos \nec \ex x. G(x) \imp \nec \ex x. G(x)$}\RightLabel{$\imp_E$}
		\BIC{$\nec \ex x. G(x)$} \RightLabel{$\imp_I^1$}
		\UIC{$\pos \ex z. G(z) \imp \nec \ex x. G(x)$}
\end{prooftree}
\end{small}
